% Andrey Kaipov
% Resume
% Adapated from https://github.com/moderncv/moderncv/blob/master/template.tex

\documentclass[10pt,letterpaper,sans]{moderncv} % choose a4 or letterpaper
\usepackage[vscale=.88,hscale=.80]{geometry} % page margins

\newcommand{\Fsharp}{F\nolinebreak[4]\raisebox{.4ex}{\texttt{\#}}}

\input{patches/preamble}
\moderncvstylecustom[black][awesome]{classic}{banking}
% header styles: casual, classic, undertow, banking
% body styles: classic, banking, oldstyle (banking w/o lines)

\name{Andrey}{Kaipov}
\homepage{kaipov.com}
\email{andrey@kaipov.com}
% \social[linkedin]{kaipov}
% \social[github]{andreykaipov}

\begin{document}
\makecvtitle
\vspace{-2mm}

\section{Experience}
\cventryoneline{May 2022 -- Present}{Software Engineer}{GitHub}{Miami, FL}{Remote}{
  \begin{itemize}
  \item
    Refactored our logging pipeline, specifically by breaking up the monostate
    into tinier Terraform workspaces via meticulous state surgeries, replacing
    bespoke Azure Event Hub clusters with neatly managed ones, and replacing
    legacy Kafka consumers with Azure Functions instead.
  \item
    Automated Datadog agent version upgrades across GitHub's fleet of VMs.
  \item
    Managed the migration of our macOS runners across both GitHub Actions and
    Azure DevOps, by coordinating between cloud procurement, system
    integrators, and obscure Azure teams.
  % \item
  %   Automated the bootstrapping, validation, inventory, and telemetry for the
  %   management servers, switches, and macOS hosts in our racks, working around
  %   Microsoft's endless red tape and Apple's EULA.
  % \item
  %   Created tooling to ease the management of our legacy ``trashcan Mac''
  %   racks, speeding up DRI response times.
  \end{itemize}
}
\cventryoneline{Feb 2022 -- Aug 2023}{Lead Site Reliability Engineer}{Target}{Miami, FL}{Remote}{
  \begin{itemize}
  \item
    Developed a Terraform-like tool for Target's PaaS allowing users to
    describe their applications as Kubernetes-inspired YAML manifests so that
    deployment configs could be bundled alongside code, instead of manually
    managing deployments through monotonous clicks in the UI.
  \item
    Worked on a handful of proof-of-concepts to help bring tracing to the
    organization by writing and contributing upstream a variety of custom
    OpenTelemetry processors, exporters, and extensions to adhere to Target's
    standards.
  \end{itemize}
}
\cventryoneline{June 2020 -- Feb 2022}{Senior Site Reliability Engineer}{Ultimate Kronos Group}{Weston, FL}{Remote}{
  \begin{itemize}
  \item
    Developed and maintained Terraform modules abstracting development teams'
    access to public cloud services, and created workflows to promote
    a seamless and transparent user experience transitioning from the private
    cloud system.
  \item
    Developed tooling to automate the management of volume snapshots and
    backups for our MySQL and MongoDB services
    % (which were actually nonexistent at the time)
    to meet some short-notice compliance audit deadlines.
  \item
    Worked closely with traditional Windows sysadmins and application owners to
    automate the heavily involved and manual configuration of our core products via
    Ansible playbooks, evangelizing SRE principles along the way.
  \end{itemize}
}
\cventryoneline{Jan 2020 -- June 2020}{Site Reliability Engineer}{Magic Leap}{Plantation, FL}{Hybrid}{
  \begin{itemize}
  \item
    Developed Kubernetes operators to manage GCP resources to make the migration from AWS easier.
  % \item
  %   Evangelized the technologies of our SRE sister-squads to our product
  %   teams, while helping them transition to newer company-wide standards.
  % \item
  %   Performed housekeeping across the SRE organization -- upgraded Terraform
  %   AWS and GCP modules and projects to use the latest versions, upgraded
  %   Concourse pipelines, migrated images from ECR and GCR to our private
  %   Docker registry, and added reusable features to our internal tooling.
  \end{itemize}
}
\cventryoneline{Jan 2017 -- Jan 2020}{Cloud Platform Engineer}{Ultimate Software}{Weston, FL}{Hybrid}{
  \begin{itemize}
  \item
    Developed and managed a centralized logging and metrics collection platform
    for company-wide use with Chef, ingesting over 5TB/day of logs and metrics into our
    milti-datacenter Elasticsearch and InfluxDB clusters.
  \item
    Managed several VM and container-based orchestration platforms for product
    teams to leverage, including a homegrown PaaS, on-prem Pivotal Cloud Foundry,
    and on-prem Kubernetes clusters.
  % \item
  %   Partnered with product teams to help developers learn our infrastructure and
  %   internal tooling, and how best to productionalize their applications and
  %   processes.
  \item
    Did all the other silly SRE things, e.g. automated toil away, tracked
    outages, conducted postmortems, troubleshot all kinds of systems, woke up at
    4am because someone from the NOC called the wrong number by accident.
  \end{itemize}
}
\cventryoneline{Summer 2016}{Software Engineer Intern}{Best Buy}{Richfield, MN}{On-site}{}

\section{Skills}
\cventryskill{Languages}
  {Go, Shell, Python, JavaScript, TypeScript, Ruby, Java, Kotlin, \Fsharp{}, Lisp, \LaTeX.}
\cventryskill{Tooling}
  {Terraform, Vault, Packer, Docker, Ansible, Chef, Bosh, Concourse.}
% \cventryskill{Services}
  % {MySQL, MongoDB, Redis, RabbitMQ.}
\cventryskill{Platforms}
  {Linux, Kubernetes, Cloud Foundry, OpenStack, Azure, GCP, AWS.}
\cventryskill{Observability}
  {Datadog, Elasticsearch, Logstash, Kibana, Fluent Bit, InfluxDB, Telegraf, Grafana, Sensu.}

\section{Projects}
\cventryproject{kaipov.com}{goobs}                                   % repo:andreykaipov/goobs
  {Go client library to control OBS Studio.}
% \cventryproject{kaipov.com}{env2conf}                                % repo:andreykaipov/env2conf
  % {Convert environment variables into configuration.}
\cventryproject{kaipov.com}{funcopgen}                               % repo:andreykaipov/funcopgen
  {Generate functional options for your Go structs.}
\cventryproject{kaipov.com}{mongodb-pool}                            % repo:andreykaipov/mongodb-pool
  {Manage MongoDB connection pools with less headaches.}
\cventryproject{kaipov.com}{tf-chef-solo}                            % repo:andreykaipov/terraform-provisioner-chef-solo
  {Chef Solo provisioner for Terraform, inspired by the Packer one.}
\cventryproject{kaipov.com}{active-standby}                          % repo:andreykaipov/active-standby-controller
  {Kubernetes controller supporting active/standby applications.}

\section{Education}
\cventryoneline{Aug 2013 -- Dec 2016}{BS in Mathematics \& Computer Science}{Florida International University}{Miami, FL}{}{
  Honors: Summa Cum Laude, Phi Beta Kappa, FIU Ambassador Scholar, Florida Academic Scholar.
}

\end{document}
